{\setstretch{1.0}
\begin{thebibliography}{25}


\bibitem{saraee_et_al}
M. Saraee, S. White \& J. Eccleston, “A data mining approach to analysis and prediction of movie ratings”, University of Salford, England, The Fifth International Conference on Data Mining, Text Mining and their Business Applications, 15-17 September 2004, pp 344- 352.

\bibitem{role_factors_prediction_movie}
Bhave, A., Kulkarni, H., Biramane, V., \& Kosamkar, P. (2015, January). Role of different factors in predicting movie success. In 2015 International Conference on Pervasive Computing (ICPC) (pp. 1-4). IEEE.
 
\bibitem{actors_factor}
Wallace, W. T., Seigerman, A., \& Holbrook, M. B. (1993). The role of actors and actresses in the success of films: How much is a movie star worth?. Journal of cultural economics, 1-27.

\bibitem{star_factor}
De Vany, A., \& Walls, W. D. (1999). Uncertainty in the movie industry: Does star power reduce the terror of the box office?. Journal of cultural economics, 23(4), 285-318.

\bibitem{movie_success_problem}
Sharda, R., \& Delen, D. (2006). Predicting box-office success of motion pictures with neural networks. Expert Systems with Applications, 30(2), 243-254.

\bibitem{movie_forecastin_dnn}
Ghiassi, M., Lio, D., \& Moon, B. (2015). Pre-production forecasting of movie revenues with a dynamic artificial neural network. Expert Systems with Applications, 42(6), 3176-3193.

\bibitem{movie_forecasting_bpnn}
Zhang,  L.,  Luo,  J.,  \&  Yang,  S.  (2009).  Forecasting  box  office  revenueof movies with BP neural network. Expert Systems with Applications,36(3), 6580-6587.

\bibitem{statista_movies_released}
Statistics of movies released since 2001, https://www.statista.com/statistics/187122/movie-releases-in-north-america-since-2001/, visited online on January 25th, 2020

\bibitem{ltc}
Varol, G., Laptev, I., \& Schmid, C. (2017). Long-term temporal convolutions for action recognition. IEEE transactions on pattern analysis and machine intelligence, 40(6), 1510-1517.
 
\bibitem{lstm}
Hochreiter, S., \& Schmidhuber, J. (1997). Long short-term memory. Neural computation, 9(8), 1735-1780.

\bibitem{resnet}
K. He, X. Zhang, S. Ren and J. Sun, "Deep Residual Learning for Image Recognition," 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), Las Vegas, NV, 2016, pp. 770-778.

\bibitem{imdb}
Internet Movie Database, https://www.imdb.com/interfaces/, accessed online March 17th

\bibitem{kim_et_al}
T. Kim, J. Hong, and P. Kang. (2015). Box office forecasting using machine learning algorithms based on SNS data.

\bibitem{travis_et_al}
Travis Ginmu Rhee and Farhana Zulkernine. 2016. Predicting movie box office profitability: a neural network approach. In 2016 15th IEEE International Conference on Machine Learning and Applications (ICMLA), pages 665–670. IEEE.

\bibitem{sameer_et_al}
Sameer Ranjan Jaiswal and Divyansh Sharma. 2017. Predicting success of bollywood movies using machine learning techniques. In Proceedings of the 10th Annual ACM India Compute Conference on ZZZ, pages 121–124. ACM.

\bibitem{chen_a}
A. Chen, “Forecasting gross revenues at the movie box office,” Working paper, University of Washington Seattle, WA, June 2002.
 
\bibitem{winners_and_loosers}
Simonoff, J. S., \& Sparrow, I. R. (2000). Predicting movie grosses: Winners and losers, blockbusters and sleepers. Chance, 13(3), 15-24.

\bibitem{shawney_et_al}
M. S. Sawhney and J. Eliashberg, “A parsimonious model for forecasting gross box-office revenues of motion
pictures,” Marketing Science, vol. Vol. 15, No. 2, pp.
113–131, 1996.

\bibitem{Sitaram_Asur}
Sitaram Asur and Bernardo A. Huberman, “Predicting the Future with Social Media,” http://arxiv.org/abs/1003.5699, March 2010.

\bibitem{reddy_et_al}
Reddy, A. S. S., Kasat, P., \& Jain, A. (2012). Box-office opening prediction of movies based on hype analysis through data mining. International Journal of Computer Applications, 56(1), 1-5.

\bibitem{Nahid_Quader}
Quader, N., Gani, M. O., \& Chaki, D. (2017, December). Performance evaluation of seven machine learning classification techniques for movie box office success prediction. In 2017 3rd International Conference on Electrical Information and Communication Technology (EICT) (pp. 1-6). IEEE.

\bibitem{apala_et_al}
Apala, K. R., Jose, M., Motnam, S., Chan, C. C., Liszka, K. J., \& de Gregorio, F. (2013, August). Prediction of movies box office performance using social media. In 2013 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2013) (pp. 1209-1214). IEEE.

\bibitem{Yao_zhou}
Zhou, Y., Zhang, L., \& Yi, Z. (2019). Predicting movie box-office revenues using deep neural networks. Neural Computing and Applications, 31(6), 1855-1865.

\bibitem{ozkan_et_al}
K. Ozkan, O. N. Atak, and S. Işik. "Using movie posters for prediction of box-office revenue with deep learning approach." 2018 26th Signal Processing and Communications Applications Conference (SIU). IEEE, 2018.

\bibitem{gevaria_et_al}
Gevaria, K., Wagh, R., \& D'mello, L.R. (2015). Movie Attendance Prediction.

\bibitem{mashall_et_all}
Marshall, P., Dockendorff, M., \& Ibanez, S. (2013). A forecasting system for movie attendance.

\bibitem{zhang_et_al}
Zhang, Xu., Hou, Guangming., Dong, Weijia., Modelling movie attendance with seasonality: evidence from China, Applied Economics Letters. Nov2017, Vol. 24 Issue 19, p1351-1357. 7p. 

\bibitem{merlin_20fox}
Hsieh, C., Campo, M., Taliyan, A., Nickens, M., Pandya, M., \& Espinoza, J.J. (2018). Convolutional Collaborative Filter Network for Video Based Recommendation Systems. ArXiv, abs/1810.08189.

\bibitem{campo_et_al}
Miguel Campo, Cheng-Kang Hsieh, Matt Nickens, J. J. Espinoza, Abhinav Taliyan, Julie Rieger, Jean Ho, Bettina Sherick:
Competitive Analysis System for Theatrical Movie Releases Based on Movie Trailer Deep Video Representation. CoRR abs/1807.04465 (2018)

\bibitem{Wang_et_al}
H. Wang, N. Wang, and D.-Y. Yeung. Collaborative
deep learning for recommender systems. In
Proceedings of the 21th ACM SIGKDD International
Conference on Knowledge Discovery and Data Mining,
pages 1235–1244. ACM, 2015

\bibitem{Li_et_al}
X. Li and J. She. Collaborative variational
autoencoder for recommender systems. In Proceedings
of the 23rd ACM SIGKDD International Conference
on Knowledge Discovery and Data Mining, pages
305–314. ACM, 2017

\bibitem{ilsvrc_15}
The ILSVRC 2015 ImageNet Competition, http://image-net.org/challenges/LSVRC/2015/, accessed online March 3rd, 2020

\bibitem{coco_19}
Coco competition, http://cocodataset.org/home, accessed online March 3rd, 2020

\bibitem{rnn}
Rumelhart, David E.; Hinton, Geoffrey E.; Williams, Ronald J. (1986-10-09). "Learning representations by back-propagating errors". Nature. 323 (6088): 533–536. doi:10.1038/323533a0. ISSN 1476-4687.

\bibitem{movie_trailer_types}
Finsterwalder, J., Kuppelwieser, V.G., de Villiers, M. (2012) The effects of film trailers on shaping consumer expectations in the entertainment industry—A qualitative analysis. Journal of Retailing and Consumer Services, 19(6), pp. 589-595.
 
\bibitem{kernel_dimension}
D. Tran, L. Bourdev, R. Fergus, L. Torresani, and M. Paluri, “Learning spatiotemporal features with 3D convolutional networks,” in ICCV, 2015.

\bibitem{adam_optimizer}
Adam: A Method for Stochastic Optimization
D. Kingma, and J. Ba.(2014) Published as a conference paper at the 3rd International Conference for Learning Representations, San Diego, 2015.

\bibitem{imagenet}
ImageNet dataset link, http://www.image-net.org/, visited on February 2nd, 2020 

\bibitem{chen_gross_revenues}
Chen, A. (2002). Forecasting gross revenues at the movie box office. University of Washington, Seattle.
 
\bibitem{lash_et_al}
Lash, M. T., \& Zhao, K. (2016). Early predictions of movie success: The who, what, and when of profitability. Journal of Management Information Systems, 33(3), 874-903.
  
\bibitem{Simonyan_et_al}
Simonyan, K., \& Zisserman, A. (2014). Two-stream convolutional networks for action recognition in videos. In Advances in neural information processing systems (pp. 568-576).


% \bibitem{Karpathy_et_al}
% Karpathy, A., Toderici, G., Shetty, S., Leung, T., Sukthankar, R., \& Fei-Fei, L. (2014). Large-scale video classification with convolutional neural networks. In Proceedings of the IEEE conference on Computer Vision and Pattern Recognition (pp. 1725-1732).
 
% \bibitem{wang_et_al}
% Wang, L., Xiong, Y., Wang, Z., \& Qiao, Y. (2015). Towards good practices for very deep two-stream convnets. arXiv preprint arXiv:1507.02159.


% \bibitem{Feichtenhofer_et_al}
% Feichtenhofer, C., Pinz, A., \& Zisserman, A. (2016). Convolutional two-stream network fusion for video action recognition. In Proceedings of the IEEE conference on computer vision and pattern recognition (pp. 1933-1941).
 
% \bibitem{tran_et_al}
% Tran, D., Bourdev, L., Fergus, R., Torresani, L., \& Paluri, M. (2015). Learning spatiotemporal features with 3d convolutional networks. In Proceedings of the IEEE international conference on computer vision (pp. 4489-4497).
 
\bibitem{ji_et_al}
Ji, S., Xu, W., Yang, M., \& Yu, K. (2012). 3D convolutional neural networks for human action recognition. IEEE transactions on pattern analysis and machine intelligence, 35(1), 221-231.
 
\bibitem{taylor_et_al}
Taylor, G. W., Fergus, R., LeCun, Y., \& Bregler, C. (2010, September). Convolutional learning of spatio-temporal features. In European conference on computer vision (pp. 140-153). Springer, Berlin, Heidelberg.

\end{thebibliography}
}